Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-04 report/report.tex
Update todo
Format citations to provide references

Virtual cities has in recent years been a popular research topic in the field of computer visualization.
The idea of recreating real world cities in 3D applications has a growing number of applications, including visualization and modelling, urban planning and architecture, as well as entertainment in the form of video games and 3D animation.
Traditionally, modelling virtual cities is a labour-intensive and time-consuming task.
However, in recent years there has been major research work in the field of procedural content generation, meaning automatic or semi automatic generation of 3D models without the direct involvment of a 3D artist.
Such methods can indeed be used in the field of virtual city reproduction to reduce the labour required to reproduce accurate 3D representations of cities, but the field of procedual city reproduction comes with its own host of challenges.
Urban environments are typically dense and large, spanning a few to hundreds of square kilometers, and are influenced by variables that are hard to quantify, including land policies, government plans, population changes and transportation infrastructure.
\textbf{(Vanegas et al, 2010)}.

@@

Cities consist of complex collections of \textbf{buildings}, \textbf{blocks}, \textbf{parcels} and \textbf{neighbourhoods} which are all interconnected via a \textbf{street} network, where individual streets can serve different types of traffic.
These features are commonly represented as \textbf{geodata} in map databases, and processed and organized into visualization-ready data by a \textbf{Geographic Information System (GIS)}.
In practise, cities are often made up out of many square kilometers worth of geodata, and it would be highly labour intensive to recreate all the features in 3D.
Instead, \textbf{procedural models} for city reproduction instead rely on programmatic solutions for converting map data to 3D road and building models, and composing them to a 3D world that the designer may continue to fine-tweak through interfaces fo interactive editing.
At the very base of this process is the procedural layout of road networks in 3D,
\textbf{(Müller et al, 2006)}
and so far there have been a lot of research in modelling of 3D road networks, but these projects have often focused on the road networks designated for cars and public transit, as a part of the sustainable mobility paradigm and the topic of sustainable cities, particularily due to the interest in self-propelled cars.
The study of energy efficient mobility such as walking and cycling is only in its emerging phase. \textbf{(Stojanovski, 2019)}

@@

The project falls within the broader topic of geodata extraction and modelling, primarily of roads and building parcels.
Geodata modeling is at the foundation of procedural modelling of real-world cities, since any application which models cities based on geodata will need a robust method of aqquiring and laying out road and building data without compromising the data's integrity. \textbf{(Müller et al, 2006)}

Procedural modeling of road networks is of interest to the fields of urban planning and urban architecture. In recent years there has been an advent of interactive tools that aid urban planners in placing or generating features of an urban plan, particularly roads and road networks. Procedural and AI solutions that aid the arcitect in a form of human-machine symbiosis.

Procedural city-generation models combine architectural elemets, such as streets, lots, buildings, building facades.
Urban design practises with conventional two-dimenstional deliverables range from delivering neighbourhood designs, urban zoning and building plans, to writing design codes and building ordinances.
The last decade has seen multiple startups in the area of software that aid urban arcitecture. The software uses procedural models to render a city grid based on real-world locations, or generate new user-specified parameters, and allow for varying degrees of manual editing on grid, road, neighbourhood, city block or individual feature level.
Some of the most prominent examples are ArcGIS Pro (made by Esri), CityEngine (made by the startup Procedural, bought by ESRI) and Urban Canvas (made by the startup Synthicity, bought by Autodesk, now defunct).

But such tools are as of today not commonly applied in urbanist practises, due to failures in reflecting the unique workspace of arcitects and their design needs. Urban arcitecture is a social factors, stakeholders. Each arcitect is an actor in a continously developing environment, and affecting that environment in a complex manner through their action \textbf{(Stojanovski et al, 2020)}.

In recent years, there have been an advent of tools that extract geodata from OSM and generate 3D representations of real world locations by placing terrain, buildings, roads and other features.
However, freely available such tools seldom include smaller roads and pedestrian footpaths such as walkways, sidewalks or trails.

Additionally, the topic is of interest for 3D content creators in for example the fields of video game design or 3D animation. A trend in these fields is using methods of procedural modeling to create large amounts of 3D content quickly and efficiently, while requiring as little hand modeling as possible. Studios who create large worlds are often interested in solutions that generate large road networks without any hand modeling. \textbf{(Parish and Müller, 2001)}

@@

When assessing the completeness of geodata, a very common scale is Van Oorts criteria for evaluating the quality of geographical information, which at the time of publication received attention from surveyors and cartographers.
\textbf{(Van Oort, 2006)} Since then a number of publications have examined slices of geodata from van Oort's criteria.
In 2008, \textbf{(Haklay, 2010)} conducted such a study to estimate of the quality of OSM positional geodata in London and England.
Since the OSM project started in London it was thought that OSM data in the London metropolitan area would be representative of the highest quality data available, and therefore a good indicator for the whole global OSM dataset.
The study was conducted by comparing OSM data to Ordnance Survey datasets.
The study showed that the OSM dataset had a rough positional accuracy of 6 meters from the reference dataset.
However, at the time of the study, the OSM project had captured roughly 29\% of the area of England, meaning that the data completeness was fairly low.

The next notable study to assess the quality of OSM data was published by \textbf{(Kunze, 2012)}.
The study applied different methods to assess the completeness of OSM data in two federal states in Germany, mainly by analysing the area difference between the OSM dataset and an administrative dataset.
Finally, a notable study in 2013-2014, conducted by researchers from various universities in Norway and Germany \textbf{(Fan et al, 2014)}, examined the quality and accuracy in building footprint data of the Munich area, at a time and place where the completeness of the OSM dataset was significantly higher (the results of their study showed that the OSM had captured close to 100\% of all building footprints).
At the time Munich was one of the most developed cities in OSM.
Their study included an insight in the geometrical calculations neccessary to match features and points between two datasets, and how to reliably calculate the metrics needed for the most important and assessible of van Oorts criteria.
Their study revealed that although the feature completeness of OSM was high, some architectural details were missing.
The results reveal that the positional accuracy of OSM data at the time was about 4 meters.

@@

\textbf{(Haklay, 2010)} presents a comprehesive list of 8 accuracy classes when it comes to evaluating the quality of geographic information (van Oorts criteria)

@@

The geometrical precision study has been carried out in a number of steps that are all detailed below.
First a feature map was found, which mapped individual features between the OSM dataset and a reference dataset.
A program then took matching building pairs and extracted matching geometrical points after first simplifying the polygons using the Douglas-Peucker algorithm \textbf{(Douglas and Peucker, 1973)}.
Once a set of matching points has been found across the whole dataset, the average distance between them was taken as a measure of the positional accuracy.

@@

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship.
Footprints from different datasets may be formed at a different level of detail.
Problems that arise are e.g. that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the polygon in the two datasets.
To avoid this effect, key points are extracted using the Douglas-Peucker algorithm \textbf{(Douglas and Peucker, 1973)}, to create a simplifed footprint with less points that still retain information about the rough features of the detailed footprint.
The idea behind Douglas-Peucker is to recursively divide a polyline.
It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$.
It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$.
Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded.
See Algorithm 1 for a detailed view.
In either case The Oriented Minimum Bounding Rectangle (OMBR) is calculated for the two polygons.
Finally the OMBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the OMBR of the SLU building footprint.
Any edges in the simplified footprints that coinside with the OMBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.
See figure \ref{fig:vertex-match-algo} for an illustration of the algorithm that detects matching vertices between two similar polygons.

@@

The OSM project is a wiki-like geodatabase based on Volunteered Geographical Information (VGI), meaning anyone can contribute by adding or editing features.
OSM road data and building footprints are commonly obtained by manually tracing features in commercially available satellite images.
Such images have a limit on their resolution which puts a theoretical limit on the accuracy of map features compared to their real-world equivalents (Haklay 2010).
Particularily the high resolution imagery from Bing in 2010 led to an increase in building information in OSM, and the positional error is largely due to the limited resolution in such satellite imagery. \textbf{(Fan et al, 2014)}.

@@

% Internet:
% TODO: Switch to numerical citations
% TODO: Add source of image on page 1

@@

As has been mentiond in the introduction to this report, procedural generaion of road networks is a basal requirement for quick and low-effort modeling virtual cities.
Since the road network ties together the city, and forms the grid that divides the lots, quarters and neighbourhoods, it make sense that one can only continue with the remaining challenges once there exists a robust procedure for extracting road geodata and generating the 3D represention of it without compromising the data integrity. 
The same is true for building modelling.
It turns out that the same methods that have been used in this project to obtain and qualify road network data can be applied to building footprint data from OSM. \textbf{(Fan et al, 2014)}
And only when there exists such a fundamental procedure for accuratly importing building footprints without compromising the data integritey, one can proceed with the remaining challenges in building modeling. \textbf{(Müller et al, 2006)}

@@

Another crucial concept in city modelling is the Level Of Detail (LOD) aspect.
LOD is a definition of a series of different 3D representation of the same data, at different detail levels, and the LOD chosen for a particulary application suggests how the data has been aqquired and modelled.
The CityGML standard divides the LOD representation of 3D models into three classes: A B and C.
\begin{enumerate}
    \item LOD-A models are renderings of the building footprint itself, or rectangular building blocks that have been extruded from the footprint to give the building height.
    \item LOD-B models are building blocks with simplifed roof shapes.
    \item LOD-C models are LOD-B models which include features such as doors, windows, alcoves, building decor, indoor features or vegetation.
\end{enumerate}
\textbf{(Biljecki et al, 2016)}
A modeler may chose what LOD class(es) to use depending on data availablity and application.
It turns out that, with the current means of data aquisition from OSM being limited to building footprints, using OSM data a model can only produce LOB-B models at best.
If a modeler wishes to aqquire building assets at a LOD-C level, they would have to complete the data with other sources, or rely on procedural methods to populate crude city models with additional details and building features that give the models more aestethic depth, but do not neccessarily reflect reality.

@@

Procedural techniques are, as mentioned, methods for reconstructing or creating 3D automatically, with minimal manual work required. Adding such techniques for content creation into the workflow of city reconstruction will increase the level of detail that is possible, while sacrificing accuracy to the real-world.
\textbf{(Mũller et al, 2006)} present how to accomplish this using Shape Grammar: a method for automatically and iteratively constructing 3D models based in a hierarchical set of rules.
By starting with a crude volumetric model of a building and iteratively remodeling it from a set of shape grammars, a procedural model can structure the façade, add texture and add details for windows, doors and ornaments, and so on.
Shape grammars often work from a databank of 3D models and a set of hierarchical rules for how these can be pieced together.
This creates a possible generative space of many different models that can be created from the same data and rule set, and with the induction of random fluctuations, many different models can be generated from the same dataset and rules.
For simple presentation in e.g. animation and videogames or even urban planning software, such procedurally generated cities could very well be enough.
As said however, the big problem is that these features will rarely match real life, such models will be sufficient as long as one can be satisified with looking at rough representations of buildings and does not require additional knowledge about minor features.
Many studies urban development have been done before that requred detailed knowledge about a city's geometry, e.g. for the purposes of modeling heat development
\textbf{(Nakata-Osaki, Souza and Rodrigues, 2018)}
and reducing noise.
\textbf{(Joon, Seo and Byung, 2011)}

\section{Feasibility in the urban planning field}
By looking at such studies in urban development, one will discover that a lot of research in this field requires detailed morpological information that goes beyond simply knowing the geometry of the city.
Urban architects often work with morpological structures where a single feature, such as a city neighbourhood, can be examined from many different levels of perspective.
A neighbourhood can be analysed from the level of its city blocks, individual lots, properties or building limits, building facades or even indoor spaces.
Simlarily a road network can be analysed by looking at it either at its connectivity by viewing it a a simple 2D graph
But it might as well be seen as a hierarchical structure where primary roads branch off into sub-streets. 
The very unfortunate fact is that much of that morpological information is not present in the OSM dataset.
Furthermore, take the fact that even a single road can be comprised of many different sections with different purposes.
A single inner-city street for example, often contains sidewalks and lanes reserved for taxis or public transit, all of a certain placement and dimension that determines what type of traffic it can serve.
This type of representation is known as a multimodal structures, due to the possibility of incorporating mulitple modes of transportation, but it may even describe subtilities like building facades and distances between curbline and building lot.
OSM, while being an excellent source of city geometry, is simply not a sophisticated enough dataset to cater to all these possible areas of research.
\textbf{(Stojanovski, 2019)}
For media applications, such morppological and multimodal information could in theory be generated procedurally, by using shape grammars and some sort of wayfinding to create logical routes for different types of traffic.
But for urban planners requiring an exact morphological representation of some specification, this complementary data will have to be obtained from another dataset.

>>>>

Virtual cities has in recent years been a popular research topic in the field of computer visualization, according to \textbf{(Vanegas et al, 2010)}.
The idea of recreating real world cities in 3D applications has a growing number of applications, including visualization and modelling, urban planning and architecture, as well as entertainment in the form of video games and 3D animation.
Traditionally, modelling virtual cities is a labour-intensive and time-consuming task.
However, in recent years there has been major research work in the field of procedural content generation, meaning automatic or semi automatic generation of 3D models without the direct involvment of a 3D artist.
Such methods can indeed be used in the field of virtual city reproduction to reduce the labour required to reproduce accurate 3D representations of cities, but the field of procedual city reproduction comes with its own host of challenges.
Urban environments are typically dense and large, spanning a few to hundreds of square kilometers, and are influenced by variables that are hard to quantify, including land policies, government plans, population changes and transportation infrastructure.

@@

In their analysis of prodedural city generation models, \textbf{(Müller et al, 2006)} provide an overview of the process of recreating virtual 3D citites from their real life conterparts.
They present cities as complex collections of \textbf{buildings}, \textbf{blocks}, \textbf{parcels} and \textbf{neighbourhoods} which are all interconnected via a \textbf{street} network, where individual streets can serve different types of traffic.
These features are commonly represented as \textbf{geodata} in map databases, and processed and organized into visualization-ready data by a \textbf{Geographic Information System (GIS)}.
In practise, cities are often made up out of many square kilometers worth of geodata, and it would be highly labour intensive to recreate all the features in 3D.
Instead, \textbf{procedural models} for city reproduction instead rely on programmatic solutions for converting map data to 3D road and building models, and composing them to a 3D world that the designer may continue to fine-tweak through interfaces fo interactive editing.
At the very base of this process is the procedural layout of road networks in 3D, and so far there have been a lot of research in modelling of 3D road networks.
\textbf{(Stojanovski, 2019)} however claims that these projects have often focused on the road networks designated for cars and public transit, as a part of the sustainable mobility paradigm and the topic of sustainable cities, particularily due to the interest in self-propelled cars.
The study of energy efficient mobility such as walking and cycling is only in its emerging phase.

@@

The project falls within the broader topic of geodata extraction and modelling, primarily of roads and building parcels.
Geodata modeling is at the foundation of procedural modelling of real-world cities (according to \textbf{(Müller et al, 2006)}), since any application which models cities based on geodata will need a robust method of aqquiring and laying out road and building data without compromising the data's integrity.
Procedural modeling of road networks is of interest to the fields of urban planning and urban architecture.
In recent years there has been an advent of interactive tools that aid urban planners in placing or generating features of an urban plan, particularly roads and road networks.
Procedural and AI solutions that aid the arcitect in a form of human-machine symbiosis.

Procedural city-generation models combine architectural elemets, such as streets, lots, buildings, building facades.
Urban design practises with conventional two-dimenstional deliverables range from delivering neighbourhood designs, urban zoning and building plans, to writing design codes and building ordinances.
The last decade has seen multiple startups in the area of software that aid urban arcitecture. The software uses procedural models to render a city grid based on real-world locations, or generate new user-specified parameters, and allow for varying degrees of manual editing on grid, road, neighbourhood, city block or individual feature level.
Some of the most prominent examples are ArcGIS Pro (made by Esri), CityEngine (made by the startup Procedural, bought by ESRI) and Urban Canvas (made by the startup Synthicity, bought by Autodesk, now defunct).
However, freely available such tools seldom include smaller roads and pedestrian footpaths such as walkways, sidewalks or trails.

Even as such tools are well available, \textbf{(Stojanovski et al, 2020)} notes that they are as of today not commonly applied in urbanist practises, due to failures in reflecting the unique workspace of arcitects and their design needs. Urban arcitecture is a social factors, stakeholders. Each arcitect is an actor in a continously developing environment, and affecting that environment in a complex manner through their action.

Finally, wen it comes to the fields of video game design or 3D animation, tools for city reproduction is undoubtedly of use to 3D content creators.
In their study of procedurally generated buildings, \textbf{(Parish and Müller, 2001)} claim that there is a widespread trend in these fields to use methods of procedural modeling to create large amounts of 3D content quickly and efficiently, while requiring as little hand modeling as possible.
Studios who create large worlds are often interested in solutions that generate large road networks without any hand modeling.

@@

When assessing the completeness of geodata, a very common scale is Van Oorts criteria for evaluating the quality of geographical information, which at the time of publication received attention from surveyors and cartographers (\textbf{(Van Oort, 2006)}).
Since then a number of publications have examined slices of geodata from van Oort's criteria.
In 2008, \textbf{(Haklay, 2010)} conducted such a study to estimate of the quality of OSM positional geodata in London and England.
Since the OSM project started in London it was thought that OSM data in the London metropolitan area would be representative of the highest quality data available, and therefore a good indicator for the whole global OSM dataset.
The study was conducted by comparing OSM data to Ordnance Survey datasets.
The study showed that the OSM dataset had a rough positional accuracy of 6 meters from the reference dataset.
However, at the time of the study, the OSM project had captured roughly 29\% of the area of England, meaning that the data completeness was fairly low.

The next notable study to assess the quality of OSM data was published by \textbf{(Kunze, 2012)}.
The study applied different methods to assess the completeness of OSM data in two federal states in Germany, mainly by analysing the area difference between the OSM dataset and an administrative dataset.
Finally, a notable study in 2013-2014, conducted by researchers from various universities in Norway and Germany (\textbf{(Fan et al, 2014)}), examined the quality and accuracy in building footprint data of the Munich area, at a time and place where the completeness of the OSM dataset was significantly higher (the results of their study showed that the OSM had captured close to 100\% of all building footprints).
At the time Munich was one of the most developed cities in OSM.
Their study included an insight in the geometrical calculations neccessary to match features and points between two datasets, and how to reliably calculate the metrics needed for the most important and assessible of van Oorts criteria.
Their study revealed that although the feature completeness of OSM was high, some architectural details were missing.
The results reveal that the positional accuracy of OSM data at the time was about 4 meters.

@@

\textbf{(Haklay, 2010)} presents in a comprehesive manner the list of van Oort's 8 accuracy classes for evaluating the quality of geographic information:

@@

The geometrical precision study has been carried out in a number of steps that are all detailed below.
First a feature map was found, which mapped individual features between the OSM dataset and a reference dataset.
A program then took matching building pairs and extracted matching geometrical points after first simplifying the polygons using the Douglas-Peucker algorithm by \textbf{(Douglas and Peucker, 1973)}.
Once a set of matching points has been found across the whole dataset, the average distance between them was taken as a measure of the positional accuracy.

@@

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship.
Footprints from different datasets may be formed at a different level of detail.
Problems that arise are e.g. that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the polygon in the two datasets.
To avoid this effect, key points are extracted using the Douglas-Peucker algorithm (\textbf{(Douglas and Peucker, 1973)}), to create a simplifed footprint with less points that still retain information about the rough features of the detailed footprint.
The idea behind Douglas-Peucker is to recursively divide a polyline.
It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$.
It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$.
Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded.
See Algorithm 1 for a detailed view.
In either case The Oriented Minimum Bounding Rectangle (OMBR) is calculated for the two polygons.
Finally the OMBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the OMBR of the SLU building footprint.
Any edges in the simplified footprints that coinside with the OMBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.
See figure \ref{fig:vertex-match-algo} for an illustration of the algorithm that detects matching vertices between two similar polygons.

@@

The OSM project is a wiki-like geodatabase based on Volunteered Geographical Information (VGI), meaning anyone can contribute by adding or editing features.
OSM road data and building footprints are commonly obtained by manually tracing features in commercially available satellite images.
Such images have a limit on their resolution which puts a theoretical limit on the accuracy of map features compared to their real-world equivalents
The driving force behind the availablity of VGI is, according to \textbf{(Fan et al, 2014)}, the availablity of high resolution satellite imagery to private individuals. They claim that particularily the imagery from Bing Maps, which launched in 2010, led to an increase in building information in OSM, and the positional error is largely due to the limited resolution in such satellite imagery.

@@

@@

As has been mentiond in the introduction to this report, procedural generaion of road networks is a basal requirement for quick and low-effort modeling virtual cities.
Since the road network ties together the city, and forms the grid that divides the lots, quarters and neighbourhoods, it make sense that one can only continue with the remaining challenges once there exists a robust procedure for extracting road geodata and generating the 3D represention of it without compromising the data integrity. 
The same is true for building modelling.
As \textbf{(Fan et al, 2014)} notes, it turns out that the same methods that have been used in this project to obtain and qualify road network data can be applied to building footprint data from OSM. 
And only when there exists such a fundamental procedure for accuratly importing building footprints without compromising the data integritey, one can proceed with the remaining challenges in building modeling.

@@

Another crucial concept in city modelling is the Level Of Detail (LOD) aspect.
\textbf{(Biljecki et al, 2016)} provide an extensive overview of the concept of LOD in GIS mapping.
They provide the GityGML definition of LOD as a series of different 3D representation of the same data, at different detail levels, and the LOD chosen for a particulary application suggests how the data has been aqquired and modelled.
The CityGML standard divides the LOD representation of 3D models into three classes: A B and C.
\begin{enumerate}
    \item LOD-A models are renderings of the building footprint itself, or rectangular building blocks that have been extruded from the footprint to give the building height.
    \item LOD-B models are building blocks with simplifed roof shapes.
    \item LOD-C models are LOD-B models which include features such as doors, windows, alcoves, building decor, indoor features or vegetation.
\end{enumerate}
A modeler may chose what LOD class(es) to use depending on data availablity and application.
It turns out that, with the current means of data aquisition from OSM being limited to building footprints, using OSM data a model can only produce LOB-B models at best.
If a modeler wishes to aqquire building assets at a LOD-C level, they would have to complete the data with other sources, or rely on procedural methods to populate crude city models with additional details and building features that give the models more aestethic depth, but do not neccessarily reflect reality.

@@

Procedural techniques are, as mentioned, methods for reconstructing or creating 3D automatically, with minimal manual work required. Adding such techniques for content creation into the workflow of city reconstruction will increase the level of detail that is possible, while sacrificing accuracy to the real-world.
\textbf{(Mũller et al, 2006)} present how to accomplish this using Shape Grammar: a method for automatically and iteratively constructing 3D models based in a hierarchical set of rules.
By starting with a crude volumetric model of a building and iteratively remodeling it from a set of shape grammars, a procedural model can structure the façade, add texture and add details for windows, doors and ornaments, and so on.
Shape grammars often work from a databank of 3D models and a set of hierarchical rules for how these can be pieced together.
This creates a possible generative space of many different models that can be created from the same data and rule set, and with the induction of random fluctuations, many different models can be generated from the same dataset and rules.
For simple presentation in e.g. animation and videogames or even urban planning software, such procedurally generated cities could very well be enough.
As said however, the big problem is that these features will rarely match real life, such models will be sufficient as long as one can be satisified with looking at rough representations of buildings and does not require additional knowledge about minor features.
Many studies urban development have been done before that requred detailed knowledge about a city's geometry, e.g. for the purposes of modeling heat development
(\textbf{(Nakata-Osaki, Souza and Rodrigues, 2018)})
and reducing noise
(\textbf{(Joon, Seo and Byung, 2011)}).

\section{Feasibility in the urban planning field}
By looking at such studies in urban development, one will discover that a lot of research in this field requires detailed morpological information that goes beyond simply knowing the geometry of the city.
Urban architects often work with morpological structures where a single feature, such as a city neighbourhood, can be examined from many different levels of perspective.
A neighbourhood can be analysed from the level of its city blocks, individual lots, properties or building limits, building facades or even indoor spaces.
Simlarily a road network can be analysed by looking at it either at its connectivity by viewing it a a simple 2D graph
But it might as well be seen as a hierarchical structure where primary roads branch off into sub-streets. 
The very unfortunate fact is that much of that morpological information is not present in the OSM dataset.
Furthermore, take the fact that even a single road can be comprised of many different sections with different purposes.
A single inner-city street for example, often contains sidewalks and lanes reserved for taxis or public transit, all of a certain placement and dimension that determines what type of traffic it can serve.
According to \textbf{(Stojanovski, 2019)}, this type of representation is known as a multimodal structures, due to the possibility of incorporating mulitple modes of transportation, but it may even describe subtilities like building facades and distances between curbline and building lot.
OSM, while being an excellent source of city geometry, is simply not a sophisticated enough dataset to cater to all these possible areas of research.
For media applications, such morppological and multimodal information could in theory be generated procedurally, by using shape grammars and some sort of wayfinding to create logical routes for different types of traffic.
But for urban planners requiring an exact morphological representation of some specification, this complementary data will have to be obtained from another dataset.
